%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {WEO {\enskip\cdotp\enskip}weo-water.com} % Organization
    {Luxembourg, Luxembourg} % Location
    {Apr. 2022- Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Setup processing pipelines spreading over multiple CPUs, running on Airflow}
        \item {Design and enhance system architecture, APIs and backends}
        \item {Work on migration to AWS CLoud Services}
        \item {Enhance and optimize processing pipelines for efficiency and stability}
        \item {Implement standards into the architecture}
        \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {Doctena S.A.{\enskip\cdotp\enskip}doctena.com} % Organization
    {Luxembourg, Luxembourg} % Location
    {Sep. 2017 ‑ Dec 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Work on monolithic legacy system, defining architecture for switch to a microservices’ architecture}
        \item {Increase system stability and site reliability through monitoring system metrics and setting up an alerting system}
        \item {Identify performance bottlenecks throughout the system, enhancing slow queries, improve coding issues and system design}
        \item {Lead and coach team of developer}
        \item {Decrease time to fix for bug reports, by automating deployment and test pipelines throughout different teams and services}
        \item {Develop and release a highly scalable vaccination platform for Brussels on time (spring 2021) within a challenging timeframe, the platform had to integrate with Doctena’s own API and be able to scale up quickly to millions of requests}
        \item {Design, document, develop and maintain internal and external APIs}
        \item {Identify business needs and write developer stories}
        \item {Notable technologies: Grails, Groovy, Java, NodeJs, Pipeline automation (CircleCi), Serverless framework, AWS, AWS Lambda, AWS DynamoDb,
NextJS, ReactJS, AngularJs, TypeScript, NodeJs, ExpressJS, Docker...}
        \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Co-founder \& Software Developer} % Job title
    {Eevol sarl{\enskip\cdotp\enskip}eevol.lu} % Organization
    {Luxembourg, Luxembourg} % Location
    {Oct. 2012 - Sept. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Bootstrap a software development company in Luxembourg, offering complete solution to develop Web and Mobile (Android/iOS) applications and software consultation}
        \item {Grew to 6 developers with a Teal Organisation}
        \item {Work with customers directly to develop application from A to Z, product description, development and running in production mode}
        \item {Work as freelance for customers in Luxembourg to offer FrontEnd and Backend development skills}
        \item {Notable technologies: AWS (Cloudformation, RDS, EC2), Docker, Grails, Groovy, Django (Python), Android, iOS development, Jenkins, AngularJs, ReactJS}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {Oashi sarl{\enskip\cdotp\enskip}oashi.com} % Organization
    {Rosport, Luxembourg} % Location
    {Sep. 2010 ‑ Sep. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Working with an internal framework based on NetRexx (JVM) and Postgres}
        \item {Implementing web based interfaces for the backend, for example: an e‑commerce platform and a process management and validation application}
        \item {Notable technologies Grails, jQuery, JavaScript, Postgres, NetRexx}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {VOLUNTEER AND TECHNiCAL ADViSOR} % Job title
    {EIRENE Suisse{\enskip\cdotp\enskip}eirene.ch} % Organization
    {Sahr, Chad} % Location
    {Jan. 2009 ‑ Jul. 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {As a technical advisor I worked on field in Sarh, Chad for 18 months to reinforce on place teachers to bootstrap a local computer school. The school was open for anyone that wanted to learn working with computers.}
        \item {Train local teachers, motivate and coach them to become independent teachers}
        \item {Work on a system to make the local school financially independent from external funds}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {Liip (former Mediagonal){\enskip\cdotp\enskip}liip.ch} % Organization
    {Fribourg, Switzerland} % Location
    {Aug. 2006 ‑ Dec. 2008} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Work as software developer at Liip on various projects, mostly PHP with Moodle and Flash applications}
        \item {iconomix.ch, develop online multiplayer games with Flash and open source streaming server Red5, responsible for developing multiplayer game protocol}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Assitant, PhD Candidate} % Job title
    {Université de Fribourg{\enskip\cdotp\enskip}unifr.ch} % Organization
    {Fribourg, Switzerland} % Location
    {Oct. 2004 ‑ Dec. 2008} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Research assistant to Prof. Dr. Ulrich Ultes‑Nitsche in the department of Telecommunication, Network and Security group at the Computer Science Department}
        \item {Research in field of Model Checking, Buechi Automata, Infinite Languages and non‑terminating systems}
        \item {Assistant to lectures of Formal Methods}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Under-Assitant} % Job title
    {Université de Fribourg{\enskip\cdotp\enskip}unifr.ch} % Organization
    {Fribourg, Switzerland} % Location
    {Oct. 2003 ‑ Jun. 2004} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Help out in the department of computer science with various tasks}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
